	
First and foremost, I must express my warmest gratitude to my supervisors, Roberto Cipolla, Tae-Kyun Kim and Oliver Woodford, for their magnificent guidance. I could not have asked for better support and inspiration, and working with them has been a great pleasure.  

My study at Cambridge would have been far less fruitful without my colleagues in the Machine Intelligence Laboratory, including Krisada, Simon, Rob, Paul, Ignas, Yu Chen, Vijay, Ujwal, Fabio, Neill, Jonathan, Weixun and Sukrit. They are the most intellectually stimulating and helpful people that I have ever worked with. I would like to thank the members in Toshiba Cambridge Research Laboratory for their help and support. I wish to thank Danhang Tang and other members in the computer vision group of Imperial College London for our collaboration and friendship. I would also like to thank Y.-S. Moon, C.-S. John Lui, K.-H. Wong and Kenneth Wong. Without their advice and support, I would not have started my study at the University of Cambridge. 

Research can sometimes be difficult, yet I am lucky to have a wonderful group of friends, from far and near, who have helped me through these years. Without them, my life would have been far less creative and enjoyable. I am greatly thankful for their support and belief.  

I am immensely grateful to the Croucher Foundation and the Cambridge Overseas Trust for their generous financial support, without them my study would not have been possible. I would also like to thank the Cambridge University Engineering Department for supporting my attendance at conferences.  

Last, but by no means least, heartfelt thanks go to my family for their never-ending love and support.  

\hfill {\raggedright \Large{\textit{Tsz-Ho Yu}}}
