	This thesis is submitted to the Department of Engineering, University of Cambridge, in fulfilment of the requirements for the degree of Doctor of Philosophy. The work contained in this thesis is my own except where otherwise mentioned. Chapter \ref{chap/hand} describes a joint research project with collaborator Danhang Tang of Imperial College London, we contributed equally to the design and experiments performed in this work. Parts of the work presented in chapters \ref{chap/eval}, \ref{chap/reg}, \ref{chap/act}, \ref{chap/body} and \ref{chap/hand} appear in the following articles:
	\begin{itemize}[]
		\item Tsz-Ho Yu, Tae-Kyun Kim, and Roberto Cipolla. Real-time action recognition by spatiotemporal semantic and structural forest. \textit{In Proceedings of the British Machine Vision Conference 2010, p.51.1--52.12}, 2010 \cite{Yu2010}
		\item Tsz-Ho Yu, Oliver J. Woodford, and Roberto Cipolla. An evaluation of volumetric interest points. \textit{In Proceedings of the 2011 International Conference on 3D Imaging, Modeling, Processing, Visualization and Transmission, p.282--289}, 2011 \cite{Yu2011}
		\item Tsz-Ho Yu, Oliver J. Woodford, and Roberto Cipolla. A performance evaluation of volumetric 3d interest point detectors. \textit{International Journal of Computer Vision, volume 102 (1--3), p.180--197}, 2013 \cite{Yu2013}
		\item Tsz-Ho Yu, Tae-Kyun Kim, and Roberto Cipolla. Unconstrained monocular 3d human pose estimation by action detection and cross-modality regression forest. \textit{In Proceedings of the 2013 IEEE Conference on Computer Vision and Pattern Recognition, p.3642--3649}, 2013 \cite{Yu2013a}
		\item Danhang Tang, Tsz-Ho Yu, and Tae-Kyun Kim. Real-time articulated hand pose estimation using semi-supervised transductive regression forests. \textit{In Proceedings of the 14th IEEE International Conference on Computer Vision, p.3224--3231}, 2013 \cite{Tang2013}
	\end{itemize}

\begin{flushright}
{\Large\textit{Tsz-Ho Yu}}\\
{\Large\textit{30/09/2013}}
\end{flushright}
